### 2025-05-08 manuscript/manuscript.Rmd
Adding preliminary results skeleton

```{r setup}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
library(tidyverse)
library(ggh4x)
library(patchwork)
library(ggtext)
library(minpack.lm)

parametadata <- read_csv("metadata/parametadata.csv") %>%
  # filter(IS_type=="noIS") %>%
  filter(polarity=="pos") %>%
  filter(samp_type=="Smp") %>%
  mutate(startime=factor(startime, levels=c("Morn", "Eve"))) %>%
  mutate(depth=factor(depth, levels=c("Surf", "Deep"))) %>%
  mutate(amendment=factor(amendment, levels=c("Amm", "Nit", "Arg", "GMP"))) %>%
  arrange(amendment, depth, timepoint_num, startime) %>%
  mutate(timepoint=fct_inorder(timepoint))
peak_areas <- read_csv("targeted/all_peak_areas_w_isos.csv") %>%
  left_join(parametadata %>% distinct(filename, shortname))
all_stans <- read_csv("metadata/all_stans.csv")
maa_names <- c("Also Palythene/Usujirene?", "Shinorine?", "Mycosporine-glycine?", 
               "Palythine?", "Another Palythene/Usujirene?", "Porphyra-334?", 
               "Also Porphyra-334?", "Asterina-330?", "Palythene/Usujirene?",
               "Mycosporine-2-glycine?")
nucleo_names <- c("5-Methylcytosine", "Adenosine", "Cytidine", "Adenine", "Guanosine",
                  "Cytosine", "Hypoxanthine/Allopurinol", "Guanine", "Deoxycytidine?",
                  "Deoxyadenosine", "Deoxyguanosine?")
betaine_names <- c("beta-Alaninebetaine", "Glycine betaine", "Homarine", "Trigonelline",
                   "Choline", "Glycerophosphocholine", "Homoserine betaine?", 
                   "Threonine betaine?", "Proline betaine",
                   "(3-Carboxypropyl)trimethylammonium", "O-Acetylcarnitine", 
                   "Betonicine", "Acetylcholine", "Phosphocholine")
non_n_names <- c("Dimethylsulfonioacetate", "Dimethylsulfoniopropionate",
                 "Arsenobetaine", "Dimethylsulfoxonium propionate?", "Gonyol",
                 "2-O-alpha-D-Glucosylglycerol")
aa_names <- c("Glutamine", "Aspartic acid", "Glutamic acid/beta-Glutamic acid",
              "Asparagine", "Alanine", "Methionine", "Arginine", "Proline",
              "Lysine", "Threonine/Homoserine", "Serine", "Glycine", "Histidine",
              "Leucine/Isoleucine", "Valine", "Arginine")
bad_cmpds <- c("Melamine", "Uridine", "Itaconic acid?", "Inosine", "Dexpanthenol", 
               "Choline sulfate", "5-Hydroxyectoine", "L-Tyrosine")
samp_areas <- parametadata %>%
  filter(samp_type=="Smp") %>%
  distinct(shortname, depth) %>%
  left_join(peak_areas) %>%
  mutate(shortname=fct_inorder(shortname)) %>%
  filter(!compound_name%in%bad_cmpds) %>%
  filter(!(depth=="Deep" & compound_name%in%maa_names)) %>%
  select(-depth)
labeled_fracs <- samp_areas %>%
  mutate(labeled_frac=1-area/sum(area), .by = c("shortname", "compound_name")) %>%
  select(compound_name, iso_name, shortname, labeled_frac) %>%
  filter(str_detect(iso_name, "13C0, 15N0")) %>%
  select(-iso_name)
log_coef_df <- labeled_fracs %>%
  filter(!compound_name%in%maa_names) %>%
  left_join(parametadata %>% distinct(shortname, amendment, depth, timepoint_num)) %>%
  nest(data=c(shortname, timepoint_num, labeled_frac)) %>%
  mutate(log_fit=map(data, ~glm(.x$labeled_frac~.x$timepoint_num, family="quasibinomial")),
         coefs=map(log_fit, function(x)broom::tidy(x))) %>%
  unnest(coefs) %>%
  select(compound_name, amendment, depth, term, estimate) %>%
  pivot_wider(names_from = term, values_from = estimate) %>%
  rename(intercept=`(Intercept)`, slope=`.x$timepoint_num`) %>%
  mutate(half_max=-intercept/slope, scale=1/slope) %>%
  mutate(frac_at_T24 = 1/(1+exp(-(intercept+slope*24))))
```

@@

>>>>

```{r setup}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, eval=FALSE)
library(tidyverse)
library(ggh4x)
library(patchwork)
library(ggtext)
library(minpack.lm)
options(pillar.sigfig = 7, pillar.print_max = 100)

parametadata <- read_csv("metadata/parametadata.csv") %>%
  # filter(IS_type=="noIS") %>%
  filter(polarity=="pos") %>%
  filter(samp_type=="Smp") %>%
  mutate(startime=factor(startime, levels=c("Morn", "Eve"))) %>%
  mutate(depth=factor(depth, levels=c("Surf", "Deep"))) %>%
  mutate(amendment=factor(amendment, levels=c("Amm", "Nit", "Arg", "GMP"))) %>%
  arrange(amendment, depth, timepoint_num, startime) %>%
  mutate(timepoint=fct_inorder(timepoint))
peak_areas <- read_csv("targeted/all_peak_areas_w_isos.csv") %>%
  left_join(parametadata %>% distinct(filename, shortname))
all_stans <- read_csv("metadata/all_stans.csv")
maa_names <- c("Also Palythene/Usujirene?", "Shinorine?", "Mycosporine-glycine?", 
               "Palythine?", "Another Palythene/Usujirene?", "Porphyra-334?", 
               "Also Porphyra-334?", "Asterina-330?", "Palythene/Usujirene?",
               "Mycosporine-2-glycine?")
nucleo_names <- c("5-Methylcytosine", "Adenosine", "Cytidine", "Adenine", "Guanosine",
                  "Cytosine", "Hypoxanthine/Allopurinol", "Guanine", "Deoxycytidine?",
                  "Deoxyadenosine", "Deoxyguanosine?")
betaine_names <- c("beta-Alaninebetaine", "Glycine betaine", "Homarine", "Trigonelline",
                   "Choline", "Glycerophosphocholine", "Homoserine betaine?", 
                   "Threonine betaine?", "Proline betaine",
                   "(3-Carboxypropyl)trimethylammonium", "O-Acetylcarnitine", 
                   "Betonicine", "Acetylcholine", "Phosphocholine")
non_n_names <- c("Dimethylsulfonioacetate", "Dimethylsulfoniopropionate",
                 "Arsenobetaine", "Dimethylsulfoxonium propionate?", "Gonyol",
                 "2-O-alpha-D-Glucosylglycerol")
aa_names <- c("Glutamine", "Aspartic acid", "Glutamic acid/beta-Glutamic acid",
              "Asparagine", "Alanine", "Methionine", "Arginine", "Proline",
              "Lysine", "Threonine/Homoserine", "Serine", "Glycine", "Histidine",
              "Leucine/Isoleucine", "Valine", "Arginine")
bad_cmpds <- c("Melamine", "Uridine", "Itaconic acid?", "Inosine", "Dexpanthenol", 
               "Choline sulfate", "5-Hydroxyectoine", "L-Tyrosine")
samp_areas <- parametadata %>%
  filter(samp_type=="Smp") %>%
  distinct(shortname, depth) %>%
  left_join(peak_areas) %>%
  mutate(shortname=fct_inorder(shortname)) %>%
  filter(!compound_name%in%bad_cmpds) %>%
  filter(!(depth=="Deep" & compound_name%in%maa_names)) %>%
  select(-depth)
labeled_fracs <- samp_areas %>%
  mutate(labeled_frac=1-area/sum(area), .by = c("shortname", "compound_name")) %>%
  select(compound_name, iso_name, shortname, labeled_frac) %>%
  filter(str_detect(iso_name, "13C0, 15N0")) %>%
  select(-iso_name)
log_coef_df <- labeled_fracs %>%
  filter(!compound_name%in%maa_names) %>%
  left_join(parametadata %>% distinct(shortname, amendment, depth, timepoint_num)) %>%
  nest(data=c(shortname, timepoint_num, labeled_frac)) %>%
  mutate(log_fit=map(data, ~glm(.x$labeled_frac~.x$timepoint_num, family="quasibinomial")),
         coefs=map(log_fit, function(x)broom::tidy(x))) %>%
  unnest(coefs) %>%
  select(compound_name, amendment, depth, term, estimate) %>%
  pivot_wider(names_from = term, values_from = estimate) %>%
  rename(intercept=`(Intercept)`, slope=`.x$timepoint_num`) %>%
  mutate(half_max=-intercept/slope, scale=1/slope) %>%
  mutate(frac_at_T24 = 1/(1+exp(-(intercept+slope*24))))

splividis <- function(n, ...){
  vir <- viridis::viridis(n, ...)
  if(n%%2==0){
    vir[as.numeric(matrix(1:n, ncol=2, byrow = TRUE))]
  } else {
    index_vec <- suppressWarnings(as.numeric(matrix(1:n, ncol=2, byrow = TRUE)))
    vir[head(index_vec, -1)]
  }
}
```

@@

### Environmental context of PARAGON cruise

Make plots from Rhea's data? Would love to add her as collaborator

Maybe just ref to PARAGON synthesis paper, should include Angel's IFCB data showing mostly Hemiaulus and its disappearance over the course of the cruise

Ref to Fuyan's published paper or remake the graph here?

### Rapid uptake and use of all N substrates

```{r}
env_concs <- read_csv("targeted/final_env_concs.csv")
env_concs %>%
  mutate(mean_nm=mean(conc_nm_in_env), .by=compound_name) %>%
  arrange(desc(mean_nm)) %>%
  mutate(compound_name=ifelse(compound_name=="L-Glutamic acid/beta-Glutamic acid", "Glutamate", compound_name)) %>%
  mutate(compound_name=ifelse(compound_name%in%unique(compound_name)[1:19], compound_name, "Other")) %>%
  mutate(compound_name=fct_inorder(compound_name)) %>%
  summarise(conc_nm=sum(conc_nm_in_env), .by=c(compound_name, filename)) %>%
  left_join(parametadata) %>%
  ggplot(aes(x=tripl, y=conc_nm, fill=compound_name)) +
  geom_col(color="black", width=1) +
  facet_nested(depth+startime~amendment+timepoint, switch="x") +
  scale_y_continuous(expand=expansion(mult=c(0, 0.1))) +
  scale_fill_manual(values = c(splividis(19), "grey")) +
  labs(x=NULL, y="Unlabeled concentrations (nM)", fill=NULL) +
  theme_bw() +
  theme(
    panel.spacing.x = unit(0, "lines"),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )
```

```{r}
peak_areas %>%
  filter(!str_detect(iso_name, "13C0, 15N0")) %>%
  filter(!compound_name%in%c("Urea", "L-Valine", "Oxalic acid", "Malic acid", 
                             "Acetylcholine", "Homarine")) %>%
  left_join(parametadata %>% distinct(filename, samp_type, amendment)) %>%
  filter(samp_type=="Smp") %>%
  left_join(read_csv("targeted/rf_df.csv")) %>%
  mutate(conc_nm=area/rf) %>%
  filter(!is.na(conc_nm)) %>%
  mutate(mean_nm=mean(conc_nm), .by=compound_name) %>%
  arrange(desc(mean_nm)) %>%
  mutate(compound_name=ifelse(compound_name=="L-Glutamic acid/beta-Glutamic acid", 
                              "Glutamate", compound_name)) %>%
  mutate(compound_name=ifelse(compound_name%in%unique(compound_name)[1:19], 
                              compound_name, "Other")) %>%
  mutate(compound_name=fct_inorder(compound_name)) %>%
  summarise(conc_nm=sum(conc_nm), .by=c(compound_name, filename)) %>%
  left_join(parametadata) %>%
  ggplot(aes(x=tripl, y=conc_nm, fill=compound_name)) +
  geom_col(color="black", width=1) +
  facet_nested(depth+startime~amendment+timepoint, switch="x") +
  scale_y_continuous(expand=expansion(mult=c(0, 0.1))) +
  scale_fill_manual(values = c(splividis(19), "grey")) +
  labs(x=NULL, y="Unlabeled concentrations (nM)", fill=NULL) +
  theme_bw() +
  theme(
    panel.spacing.x = unit(0, "lines"),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )
```

```{r}
cbind(
  peak_areas %>%
    # filter(iso_name=="L-Glutamine, 13C0, 15N0") %>%
    filter(iso_name=="Glycine betaine, 13C0, 15N0") %>%
    filter(str_detect(filename, "T0")) %>%
    select(filename, area),
  read_csv("targeted/wIS_areas.csv") %>%
    # filter(compound_name=="L-Glutamine") %>%
    filter(compound_name=="Glycine betaine") %>%
    filter(str_detect(filename, "T0")) %>%
    select(wIS_filename=filename, wIS_area=area)
) %>%
  # with(lm(wIS_area~area)) %>% summary()
  ggplot() +
  geom_point(aes(x=area, y=wIS_area)) +
  geom_abline(slope = 1.5, intercept = 0)
```

Total fraction of PN that was visible in metabolites, maybe big stacked barplot like usual?

Total number of compounds labeled over time (line plot?)

```{r thaa data}
thaa_quant <- read_csv("thaas/quant_data.csv")
metathaa <- read_csv("thaas/metathaa.csv") %>%
  mutate(depth=factor(depth, levels=c("Surf", "Deep"))) %>%
  mutate(startime=factor(startime, levels=c("Morn", "Eve")))
aa_ncs <- all_stans %>%
  filter(compound_type=="Amino Acid") %>%
  mutate(compound_name=str_remove(compound_name, "^L-")) %>%
  distinct(compound_name, n_C, n_N) %>%
  add_row(compound_name="Phenylalanine", n_C=9, n_N=1)

all_thaa_plot <- thaa_quant %>%
  filter(!str_detect(iso_name, "2H")) %>%
  left_join(metathaa) %>%
  filter(samp_type=="Smp") %>%
  left_join(aa_ncs) %>%
  select(filename, compound_name, iso_name, env_conc_nm, n_C, n_N) %>%
  mutate(n_N_lab=as.numeric(str_extract(iso_name, "(?<=15N)\\d+"))) %>%
  mutate(n_N_unlab=n_N-n_N_lab) %>%
  mutate(nM_N_lab=env_conc_nm*n_N_lab, nM_N_unlab=env_conc_nm*n_N_unlab) %>%
  select(filename, compound_name, iso_name, nM_N_lab, nM_N_unlab) %>%
  pivot_longer(c(nM_N_lab, nM_N_unlab)) %>%
  summarise(total_uM=sum(value)/1000, .by=c(filename, name)) %>%
  left_join(metathaa) %>%
  mutate(amendment=ifelse(timepoint=="T0", "T0", amendment)) %>%
  mutate(amendment=factor(amendment, levels = c("T0", "Amm", "Nit", "Arg", "GMP"))) %>%
  summarise(total_uM=mean(total_uM), .by=c(amendment, depth, startime, timepoint, name)) %>%
  arrange(depth, startime) %>%
  mutate(x_axis=paste(depth, startime)) %>%
  mutate(x_axis=fct_inorder(x_axis)) %>%
  ggplot(aes(x=x_axis, y=total_uM, fill=name)) +
  geom_col(color="black", width=1) +
  facet_nested(.~amendment, scales="free_y") +
  theme_bw() +
  scale_x_discrete(expand = expansion()) +
  scale_y_continuous(expand = expansion(mult=c(0, 0.05))) +
  scale_fill_manual(breaks = c("nM_N_unlab", "nM_N_lab"), values=c("grey80", "grey20"), 
                    labels=c("Unlabeled", "Labeled")) +
  labs(x=NULL, y="Total uM N in THAAs", fill=NULL) +
  theme(
    axis.text.x=element_blank()
  )

thaa_plot_data <- thaa_quant %>%
  left_join(metathaa) %>%
  filter(samp_type=="Smp") %>%
  mutate(amendment=ifelse(timepoint=="T0", "T0", amendment)) %>%
  summarise(avg_env_conc_nm=mean(env_conc_nm, na.rm=TRUE), .by=c(compound_name, iso_name, amendment, timepoint, startime, depth)) %>%
  filter(compound_name%in%c("Glutamic acid", "Arginine")) %>%
  mutate(iso_name=case_when(
    str_detect(iso_name, "13C0, 15N0")~"Unlabeled",
    str_detect(iso_name, "13C0, 15N1")~"Singly 15N labeled",
    str_detect(iso_name, "13C1, 15N0")~"Singly 13C labeled",
    str_detect(iso_name, "Glutamic acid, 13C5, 15N1")~"Fully C and N\nlabeled glutamate",
    str_detect(iso_name, "Arginine, 13C0, 15N3")~"3x 15N\nlabeled arginine",
    str_detect(iso_name, "Arginine, 13C0, 15N4")~"Fully N\nlabeled arginine",
    str_detect(iso_name, "Arginine, 13C6, 15N4")~"Fully C and N\nlabeled arginine",
    TRUE~"Other labeled"
  )) %>%
  mutate(iso_name=factor(iso_name, levels=c(
    "Unlabeled", "Singly 15N labeled", "Singly 13C labeled", 
    "3x 15N\nlabeled arginine", "Fully N\nlabeled arginine", 
    "Fully C and N\nlabeled arginine", "Fully C and N\nlabeled glutamate", 
    "Other labeled"))) %>%
  mutate(amendment=factor(amendment, levels = c("T0", "Amm", "Nit", "Arg", "GMP"))) %>%
  arrange(depth, startime) %>%
  mutate(x_axis=paste(depth, startime)) %>%
  mutate(x_axis=fct_inorder(x_axis))
cpal_breaks <- levels(thaa_plot_data$iso_name)
cpal_cols <- c("grey80", viridis::viridis(length(cpal_breaks)-2), "grey20")
arg_glut_thaa_plot <- ggplot(thaa_plot_data) +
  geom_col(aes(x=x_axis, y=avg_env_conc_nm, fill=iso_name),
           position="fill",
           color="black", width=1) +
  facet_wrap2(compound_name~amendment, ncol=5, strip = strip_nested(bleed = TRUE)) +
  theme_bw() +
  scale_x_discrete(expand = expansion()) +
  scale_y_continuous(labels=scales::label_percent(), breaks=c(0, 0.5, 1),
                     expand = expansion()) +
  scale_fill_manual(breaks = cpal_breaks, values = cpal_cols) +
  labs(x=NULL, y="Fraction labeled", fill=NULL) +
  theme(
    axis.text.x=element_text(angle=90, hjust=1, vjust = 0.5)
  )
total_thaa_gp <- all_thaa_plot / arg_glut_thaa_plot + plot_layout(heights = c(0.4, 0.6))
ggsave("total_thaa_gp.png", total_thaa_gp, device = "png", path = "manuscript/figures",
       width = 6.5, height = 5.5, units = "in", dpi = 300)
```

![](figures/total_thaa_gp.png)
  - THAAs were 30-50% of total PC (~2 uM, need actual data) and 70-100% PN (~0.35uM)
  - Maybe more labeling happening from inorganics in evening?
  - 50% turnover of arginine in proteins in 3 days per +Arg data, less at surface than deep (??)
  - 30-50% Glu/Gln turnover in proteins in one day per Amm data
  - Glutamate, proline fully labeled labeled from arginine
  - Phenylalanine, tyrosine, histidine(?) labeled from GMP
  - How is there so much nitrate labeling when I don't see that in the metabolites?

```{r thaa supplement figures}
thaa_quant %>%
  left_join(metathaa) %>%
  filter(samp_type=="Smp") %>%
  ggplot() +
  geom_col(aes(x=tripl, y=env_conc_nm, fill=compound_name), 
           color="black", width=1, position="fill") +
  facet_nested(depth+startime~amendment+timepoint) +
  scale_x_discrete(expand = expansion()) +
  scale_y_continuous(labels=scales::label_percent(), breaks=c(0, 0.5, 1),
                     expand = expansion()) +
  labs(x="Triplicate", y="Fraction labeled", fill=NULL) +
  theme_bw() +
  theme(
    axis.text.y=element_markdown(vjust=c(0, 0.5, 1))
  )

THAA_mol_C_gp <- thaa_quant %>%
  filter(!str_detect(iso_name, "2H")) %>%
  left_join(metathaa) %>%
  filter(samp_type=="Smp") %>%
  left_join(aa_ncs) %>%
  select(filename, compound_name, iso_name, env_conc_nm, n_C, n_N) %>%
  mutate(n_C_lab=as.numeric(str_extract(iso_name, "(?<=13C)\\d+"))/n_C) %>%
  mutate(n_C_unlab=n_C-n_C_lab) %>%
  mutate(nM_C_lab=env_conc_nm*n_C_lab, nM_C_unlab=env_conc_nm*n_C_unlab) %>%
  select(filename, compound_name, iso_name, nM_C_lab, nM_C_unlab) %>%
  pivot_longer(c(nM_C_lab, nM_C_unlab)) %>%
  summarise(total_uM=sum(value)/1000, .by=c(filename, name)) %>%
  left_join(metathaa) %>%
  mutate(amendment=factor(amendment, levels = c("T0", "Amm", "Nit", "Arg", "GMP"))) %>%
  ggplot(aes(x=tripl, y=total_uM, fill=name)) +
  geom_col(color="black", width=1) +
  facet_nested(depth+startime~amendment+timepoint) +
  theme_bw() +
  scale_x_discrete(expand = expansion()) +
  scale_y_continuous(expand = expansion(mult=c(0, 0.05))) +
  scale_fill_manual(breaks = c("nM_C_unlab", "nM_C_lab"), values=c("grey80", "grey20"), 
                    labels=c("Unlabeled", "Labeled")) +
  labs(x="Triplicate", y="Total C in THAAs (uM)", fill=NULL) +
  theme(
    legend.position = "top"
  )
THAA_mol_N_gp <- thaa_quant %>%
  filter(!str_detect(iso_name, "2H")) %>%
  left_join(metathaa) %>%
  filter(samp_type=="Smp") %>%
  left_join(aa_ncs) %>%
  select(filename, compound_name, iso_name, env_conc_nm, n_C, n_N) %>%
  mutate(n_N_lab=as.numeric(str_extract(iso_name, "(?<=15N)\\d+"))) %>%
  mutate(n_N_unlab=n_N-n_N_lab) %>%
  mutate(nM_N_lab=env_conc_nm*n_N_lab, nM_N_unlab=env_conc_nm*n_N_unlab) %>%
  select(filename, compound_name, iso_name, nM_N_lab, nM_N_unlab) %>%
  pivot_longer(c(nM_N_lab, nM_N_unlab)) %>%
  summarise(total_uM=sum(value)/1000, .by=c(filename, name)) %>%
  left_join(metathaa) %>%
  mutate(amendment=factor(amendment, levels = c("T0", "Amm", "Nit", "Arg", "GMP"))) %>%
  ggplot(aes(x=tripl, y=total_uM, fill=name)) +
  geom_col(color="black", width=1) +
  facet_nested(depth+startime~amendment+timepoint) +
  theme_bw() +
  scale_x_discrete(expand = expansion()) +
  scale_y_continuous(expand = expansion(mult=c(0, 0.05))) +
  scale_fill_manual(breaks = c("nM_N_unlab", "nM_N_lab"), values=c("grey80", "grey20"), 
                    labels=c("Unlabeled", "Labeled")) +
  labs(x="Triplicate", y="Total N in THAAs (uM)", fill=NULL) +
  theme(
    legend.position = "top"
  )
all_thaa_NC_gp <- guide_area() + THAA_mol_C_gp + THAA_mol_N_gp + plot_layout(guides = "collect", heights = c(0.1, 0.45, 0.45), design = c("1\n2\n3"))
ggsave("thaas/all_thaa_NC_gp.png", width=6.5, height=8)

pdf("thaas/all_cmpd_labels.pdf", width=9, height = 5)
for(cmpd_i in setdiff(unique(thaa_quant$compound_name), c("Citrulline", "Ornithine", "Taurine"))){
  print(cmpd_i)
  gp <- thaa_quant %>%
    filter(compound_name==cmpd_i) %>%
    left_join(metathaa) %>%
    drop_na() %>%
    ggplot() +
    geom_col(aes(x=tripl, y=env_conc_nm, fill=iso_name), 
             position="fill",
             color="black", width=1) +
    facet_nested(depth+startime~amendment+timepoint) +
    ggtitle(cmpd_i)
  print(gp)
}
dev.off()
```

### Universal bioavailability of ammonia at surface

The most rapid and extensive labeling was obtained during the ammonia-amended incubations of surface seawater. We observed significant labeling of glutamine, [and others] even at the T0 timepoint, indicating turnover times shorter than the time required to filter and flash-freeze the samples in liquid nitrogen (~20 minutes).

DISCUSSION: the speed at which ammonia labeling happens hints at a high flux, low concentration ammonia cycle in the surface ocean since uptake was too fast and too widespread to be a transcriptional response, indicating that they have ammonia transporters plus GS/GOGAT/GDH always active.

Synthesis rates?

Aspartate labeled faster than glutamate - discuss pool sizes

Slow labeling of osmolytes - discuss pool sizes
